TBD

### 2021-03-10 outputs/paper/paper.Rmd
123
t-test update

---
title: "TBD"
subtitle: "TBD"
author: "Yingying Zhou, Yang Wu, Xinyi Xu, Hong Pan"
thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
  toc: FALSE
bibliography: references.bib
---

@@

## T test1
```{r ttest1, echo=FALSE, fig.width=10, fig.height=3}

@@

## T test2
```{r ttest2, echo=FALSE, fig.width=10, fig.height=3}

@@

## T test3
```{r ttest3, echo=FALSE, fig.width=10, fig.height=3}

@@

>>>>

---
title: "TBD"
subtitle: "TBD"
author: "Yingying Zhou, Yang Wu, Xinyi Xu, Hong Pan"
thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
  toc: FALSE
bibliography: references.bib
editor_options: 
  chunk_output_type: inline
---

@@

## Deception Level
### T test1

```{r ttest1, echo=FALSE, fig.width=10, fig.height=3}

@@

### T test2
```{r ttest2, echo=FALSE, fig.width=10, fig.height=3}

@@

### T test3
```{r ttest3, echo=FALSE, fig.width=10, fig.height=3}

@@

## Affect Level

### T test 1
